% !TEX program = xelatex

\documentclass{resume}
\newcommand\tab[1][1cm]{\hspace*{#1}}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yiteng Guo}

\basicInfo{
  \email{guoyiteng@gmail.com} \textperiodcentered\ 
  \phone{(+1) 607-697-3627} \textperiodcentered\ 
  \linkedin[yiteng-guo]{https://www.linkedin.com/in/yiteng-guo-08a451106}}

\section{Education}
\datedsubsection{\textbf{Cornell University}, Ithaca, NY}{Aug 2016 -- May 2020}
\textit{Bachelor of Science}, Computer Science and Mathematics \quad \textbf{GPA: }4.135/4.3

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:} Java, C/C++, Python, JavaScript/TypeScript, OCaml, Objective-C, C\#, R
  \item \textbf{Libraries and Softwares:} Git, Linux, WebGL, JavaFX, jQuery, NumPy, Unity, \LaTeX
  \item \textbf{Coursework: }Data Structure, Object-Oriented Design, Analysis of Algorithms, Machine Learning, \\
  Programming Language Theory, Computer Graphics, Compilers, Computer System Organization
\end{itemize}

\section{Experience}
\datedsubsection{\textbf{Pocket Gems, Inc}, San Francisco, CA}{Jun 2018 -- Aug 2018}
\textit{Software Engineer Intern}
\begin{itemize}
  \item Designed a TCP-based remote network file system layer in C++ for Android devices.
  \item Ported an iOS mobile game engine to macOS platform.
  \item Wrote a non-network startup mode for a mobile game to provide developers with better testing experiences.
  \item Developed a graphics shader preprocessor to improve gaming performance.
\end{itemize}

\datedsubsection{\textbf{Programming Abstractions Research Group}, Cornell University}{Feb 2017 -- Present}
\textit{Research Assistant}\quad Advisor: Adrian Sampson\\
Enhanced an heterogeneous programming language, Braid, \textit{https://capra.cs.cornell.edu/braid/}
\begin{itemize}
  \item Developed Braid WebGL extensions such as framebuffer and cube textures.
  \item Assisted with development of type checking and type inference features.
  \item Created multiple Braid computer graphics demonstrations of shadow and dynamic mirror effect.
  \item Wrote a 3D web-based game engine and an example game in Braid.
\end{itemize}

\datedsubsection{\textbf{Department of Computer Science}, Cornell University}{Aug 2017 -- Present}
\textit{Teaching Assistant}\\
$-$ Introduction to Analysis of Algorithms, Fall 2018 \quad $-$ Introduction to Computer Graphics, Spring 2018\\
$-$ Object-Oriented Design and Data Structures (Honors), Fall 2017
\begin{itemize}
  \item Led a lab section to teach students course-related contents.
  \item Held office hours to ensure students understood course concepts.
  \item Evaluated homework and exams and gave feedback to students.
\end{itemize}

\section{Projects}
\datedsubsection{\textbf{Xi Compiler}\ \ \textit{Xi}, an imperative, object-oriented language}{}
\begin{itemize}
  \item Led a team of four to write a $\sim$25k lines-of-code program that compiles Xi to x64-64 assembly.
  \item Implemented many important functions including parser, type checker, optimization, and register allocation.
\end{itemize}
\datedsubsection{\textbf{caml\_sync}\ \ \textit{https://github.com/guoyiteng/caml\_sync}}{}
A DropBox-like program written in OCaml supporting incremental backup and history files retrieval
\begin{itemize}
  \item Designed the architecture of the codebase and a communication protocol between servers and clients.
  \item Built a server to store data from clients and to calculate incremental differences between versions.
\end{itemize}
\datedsubsection{\textbf{snapweb\_js}\ \ \textit{https://github.com/guoyiteng/snapweb\_js}}{}
A web-based SnapChat camera recognizing human faces and rendering face stickers on top of faces
\begin{itemize}
  \item Wrote WebGL shader programs to render several 3D stickers on human faces.
  \item Implemented a Computer Vision SolvePnP algorithm in JavaScript.
\end{itemize}

\section{Honors and Awards}
\datedline{\textit{\nth{1} Place}, \textbf{Samsung NY VR Hackathon}}{Feb 2017}
A VR application using Oculus Gear VR for Flip Classroom, https://github.com/fufjvnvnf/NYVRHack
% \datedline{\textit{\nth{2} Place}, \textbf{RoboCup Junior World Championship}}{May. 2015}
% An annual international robotics competition on fully autonomous soccer robots.


% \section{Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item GitHub: https://github.com/guoyiteng
%   \item Languages: English (professional), Mandarin (native)
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
